### 2020-09-30 README.Rmd
Update Suparna affiliation

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of International Affairs • Christopher Newport University  
[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Marriott School of Business • Brigham Young University  
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University

>>>>

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of International Affairs • Lewis & Clark College  
[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Marriott School of Business • Brigham Young University  
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University
